Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-06-24 bbbq_article.tex
Move prediction software to Methods

Also for MHC-II, there are multiple computational tools developed 
to predict epitopes,
such as using a trained neural network (\cite{nielsen2003reliable})
or a Gibbs sampling approach (\cite{nielsen2004improved}).
According to \cite{lundegaard2011prediction}, in 2011,
from a set of multiple tools, 
NetMHCIIpan (\cite{nielsen2008quantitative,karosiene2013netmhciipan})
gave rise to the most accurate predictions.
Later tools are \cite{zhang2013predicting},
\cite{trolle2014nettepi}, \cite{zhang2015accurate}
and the very recent MHCnuggets (\cite{shao2020high}).
In this study, we'll be using MHCnuggets, as it is the only FOSS tool available.

@@

There are multiple computational tools developed to detect which
parts of membrane proteins are TMH
In 2001, multiple tools to do so have been compared \cite{moller2001evaluation},
of which TMHMM \cite{krogh2001predicting} turned out to be the best.
Many other tools followed, such as 
Phobius (\cite{kall2004combined}),
ConPred II (\cite{arai2004conpred}),
MEMSAT3 (\cite{jones2007improving})
and MetaTM (\cite{klammer2009metatm}), which signals the importance
of TMH predictions. 
Contemporary tools are the closed-source MemBrain (\cite{feng2020topology}) 
and the FOSS tool PureseqTM (\cite{wang2019efficient}).
In this study, we will use PureseqTM.

@@

>>>>

@@

There are multiple computational tools developed to predict which
parts of membrane proteins are TMH

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Prediction software used}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For this research, the scientific literature was explored 
to find the most recent free and open source (FOSS) prediction software.
This was done by searching for papers that (1) reference older
prediction software, and (2) present a novel method to make predictions.
As a starting point, a review paper was used.

There are multiple computational tools developed to predict which
parts of membrane proteins are TMH
In 2001, multiple tools to do so have been compared \cite{moller2001evaluation},
of which TMHMM \cite{krogh2001predicting} turned out to be the best, yet
this software has a restrictive software license and is nearly two
decades old. Inspired on TMHMM, many other tools followed, such as 
Phobius (\cite{kall2004combined}),
ConPred II (\cite{arai2004conpred}),
MEMSAT3 (\cite{jones2007improving})
and MetaTM (\cite{klammer2009metatm}).
The most recent FOSS tool is called PureseqTM (\cite{wang2019efficient}),
which is used in this study.

Also for MHC-II, there are multiple computational tools developed 
to predict epitopes,
such as using a trained neural network (\cite{nielsen2003reliable})
or a Gibbs sampling approach (\cite{nielsen2004improved}).
According to \cite{lundegaard2011prediction}, in 2011,
from a set of multiple tools, 
NetMHCIIpan (\cite{nielsen2008quantitative,karosiene2013netmhciipan})
gave rise to the most accurate predictions.
Later tools are \cite{zhang2013predicting},
\cite{trolle2014nettepi}, \cite{zhang2015accurate}
and the very recent MHCnuggets (\cite{shao2020high}),
the latter which we will use in this study.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Prediction software written}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The R programming language is used for the complete 
experiment, including the analysis.
The complete experiment is bundled in the 'bbbq' R package,
which is dependent on 'pureseqtmr', 'mhcnuggetsr' and 'mhcnpreds',
as described below.

To be able to call, from R, the TMH prediction software 'PureseqTM',
which is written in C, the package 'pureseqtmr' has been developed. 
'pureseqtmr' allows to install 'PureseqTM' and use most of its features.
Excluded are the features that are used by the 'PureseqTM' 
developers to verify the correctness of their work.
'pureseqtmr' has been submitted to CRAN.

The R package 'mhcnuggetsr' is written to call the 
'MHCnuggets' Python package.
'mhcnuggetsr' allows to install 'MHCnuggets' and call it
to predict IC50 values for multiple MHC haplotypes that 'MHCnuggets' 
has already been trained upon.
Excluded is the feature to train 'MHCnuggets' on new data and/or other
haplotypes, as this study only needs IC50 predictions.
'mhcnuggetsr' has been submitted to CRAN.

To be able to use pre-calculated MHCnuggets
predictions (i.e. a distribution of IC50 values per haplotype, 
derived from random peptides), the 'mhcnpreds' R package has been 
developed. In practice, this is nothing more than a big look-up table.
Because the package is too big, it will not been submitted to CRAN.

To reproduce the full experiment as done in this paper,
the functions needed are bundled in the 'bbbq' R package.
This package is too specific to be submitted to CRAN.
